---
title: "Analysis of the permutations of re-anaysis flags "
output: html_notebook
---

First, we calculate the permutations we ar discussing in the paper:

```{r, collapse=TRUE}
library("knitr")
library("rmarkdown")
source("implementation.R")

# array of the flags for permutation
flags = c(
  REMOVE_DUPLICATES = 0, 
  REMOVE_TYPESCRIPT = 0,
  REMOVE_V8 = 0,
  USE_AUTHORS_INSTEAD_COMMITTERS = 0,
  UNCERTAINTY = 0
)

whitelist = c("00000", "11111")

```

Now loop over all flag permutations and execute those on the whitelist. All permutations will be stored in the `artifact/permutations` directory and identified by a string representing ther flags as numbera `1` o `0`:

```{r}
permutations = 0
fails = 0
id = -1
# now just loop over all permutations of the flags
while (!is.null(flags)) {
    ident = paste(as.integer(flags), collapse = "")
    knitEnv = nextPermutation()
    if (!is.na(whitelist) && ! ident %in% whitelist)
        next()
    if (is.null(knitEnv))
        break()
    id = id + 1
    # knit the document
    cat(paste("Executing permutation ", ident, "...\n", sep = ""))
    permutations <<- permutations + 1
    tryCatch({
        WORKING_DIR <<- paste0("./artifact/permutations/", ident)
        assign("WORKING_DIR", paste0("./artifact/permutations/", ident), knitEnv)
        rmarkdown::render("./re-analysis.Rmd", "html_document", envir = knitEnv, quiet = T, output_file = paste0("./artifact/permutations/", ident, "/main.html"), output_dir = WORKING_DIR)        
        cat("    PASS\n")
    }, error = function(e) {
        fails <<- fails + 1
        print(e)
    })
}
cat("ALL DONE.\n")
cat(paste("permutations: ", permutations, "\n", sep = ""))
cat(paste("fails:        ", fails, "\n", sep = ""))
```

When the permutaions have been geneated, we must analyze them. Clear the flags and set the working directory to permutations root:

```{r, collapse=TRUE}
flags = c(
  REMOVE_DUPLICATES = 0, 
  REMOVE_TYPESCRIPT = 0,
  REMOVE_V8 = 0,
  USE_AUTHORS_INSTEAD_COMMITTERS = 0,
  UNCERTAINTY = 0
)

WORKING_DIR = "./artifact/permutations"
```

First, get the permutation results calculated previously:

- `est` = value of the estimate
- `se` = standard error
- `pv` = `NA` if the result was not signifficant, p-value limit otherwise)

For bootstrap, we get `est`, `se` and `sig` and `sigCons` which are boolean vectors telling us whether the results were significant.

```{r}
loadPermutation = function(b, name, permutation) {
    lWeighted = read.csv(paste0(permutation, "/Data/languages_weighed.csv"))
    rownames(lWeighted) = lWeighted$X
    lWeighted = lWeighted %>% dplyr::select(-X)
    lZeroSum = read.csv(paste0(permutation, "/Data/languages_zeroSum.csv"))
    rownames(lZeroSum) = lZeroSum$X
    lZeroSum = lZeroSum %>% dplyr::select(-X)
    bootstrapFilename = paste0(permutation, "/Data/languages_bootstrap.csv")
    if (file.exists(bootstrapFilename)) {
        lBootstrap = read.csv(bootstrapFilename)
        rownames(lBootstrap) = lBootstrap$X
        lBootstrap = lBootstrap %>% dplyr::select(-X)
    } else {
        lBootstrap = NULL
    }
    # and create the result list
    list(
        name = name,
        weighted = lWeighted,
        zeroSum = lZeroSum,
        bootstrap = lBootstrap
    )
}
```

Let's now look at all permutations and loat them:

```{r}
loadAllPermutations = function(baseDir, b = baseline) {
    dirs = list.dirs(baseDir, recursive = F)
    result = list()
    for (d in dirs) {
        pName = strsplit(d, "/")
        pName = pName[[1]][[length(pName[[1]])]]
        if (nchar(pName) != length(flags))
            next()
        tryCatch({
            result[[pName]] = loadPermutation(b, pName, d)
        }, error = function(e) {
            print(e)
            cat("Permutation ", pName, "FAIL\n")
        })
    }
    cat("Total valid permutations: ", length(result))
    result
}
permutations = loadAllPermutations(WORKING_DIR)
```

Let's now create the skeleton for teh RQ1 table in the paper:

```{r}
result = baselineFSE_RQ1()
result = mergeDataFrames(result, baselineCACM_RQ1())
result = result %>% dplyr::select(FSE_coef, FSE_pv, CACM_coef, CACM_pv)

repetition = permutations[["00000"]]$weighted %>% dplyr::select(repetition_coef = coef, repetition_pv = pVal)
result = mergeDataFrames(result, repetition)

cleaned = permutations[["11111"]]$weighted %>% dplyr::select(clean_coef = coef, clean_pv = pVal, adjusted_fdr = pVal_fdr, adjusted_bonf = pVal_bonf)
result = mergeDataFrames(result, cleaned)

zeroSum = permutations[["11111"]]$zeroSum %>% dplyr::select(zeroSum_coef = coef, zeroSum_pv = pVal_bonf)
result = mergeDataFrames(result, zeroSum)

bootstrap = permutations[["11111"]]$bootstrap %>% dplyr::select(bootstrap_coef = coef, bootstrap_sig = sigCons)
result = mergeDataFrames(result, bootstrap)

result
```

And output it to the rq1 table:

```{r}
output_RQ1_table_repetition(result)
output_RQ1_table_reanalysis(result)
```

```{r}
remove(WORKING_DIR)
```

